---
title: "Section 02: Data Summaries and Displays"
author: Clint ko
date: Oct 13, 2017
#output: 
    #beamer_presentation:
    #    theme: boxes
    #    color: crane
    #    df_print: kable
    #    slide_level: 1
---
# set environment
```{r}
library(dplyr)
library(tidyr)
library(datasets)
```


# Plotting PMF/PDF and CDF

## Discrete Variable

Example: Binomial Random Variable
```{r}
samp = rbinom(n=1000,size=15,p=0.3)
freq = as.data.frame(table(samp))
```

---

Plot Probability Mass Function
```{r}
# x and y values
x = as.numeric(as.vector(freq$samp))
y = as.numeric(as.vector(freq$Freq))

# Scatter Plot
# Ref: https://stackoverflow.com/questions/24931006/r-simple-scatter-plot-with-vertical-lines
plot(x,y,pch=21,col=1,bg=2,axes=FALSE,ann=FALSE)
axis(1, at=seq(0,15,1))
axis(2, at=pretty(c(0, max(y))))
mtext("Frequency", side=2, line=2.5)
mtext("PMF of a binomial r.v.", side=3, line=0.5, adj=0, font=2)
segments(x0=x, y0=y, y1=0, col=8)
```

---

Plot Cumulative Distribution
```{r}
# create cdf function
cdf = ecdf(samp)
#x = 0:12
#y = cdf(x)

# Plot cumulative distribution function
plot(cdf,pch=20,col=1,bg=2,axes=FALSE,ann=FALSE)
axis(1, at=seq(0,15,1))
axis(2, at=pretty(c(0, 1)))
mtext("Frequency", side=2, line=2.5)
mtext("CMF of a binomial r.v.", side=3, line=0.5, adj=0, font=2)
```

## Continuous Random Variable

Example: Normal random variable
```{r}
samp = rnorm(n=1000,mean=10,sd=1)
freq = as.data.frame(table(samp))
```

---

Plot Probability Density Distribution
```{r}
# histogram
hist(samp, prob=TRUE, breaks=seq(min(samp)*0.9, max(samp)*1.1, 0.2), col="grey50")

# Density
d = density(samp)
lines(d, col="blue", lwd=2)
```

---

Plot Cumulative Distribution Function
```{r}
# create cdf function
cdf = ecdf(samp)
#x = 0:12
#y = cdf(x)

# Plot cumulative distribution function
plot(cdf,pch=20,col=1,bg=2,axes=FALSE,ann=FALSE)
axis(1, at=seq(0,15,1))
axis(2, at=pretty(c(0, 1)))
mtext("Frequency", side=2, line=2.5)
mtext("CMF of a binomial r.v.", side=3, line=0.5, adj=0, font=2)
```


---
# Horizontal, Vertial, Stacked Bar Charts

Reference
- https://www.r-bloggers.com/stacked-bar-charts-in-r/
- http://www.statmethods.net/graphs/bar.html

```{r}
counts <- table(mtcars$vs, mtcars$gear)
counts
```

---

```{r}
#
cols = c("#66c2a5","#fb8072") # green, red

#
barplot(
    counts, 
    main="Car Distribution by Gears and VS",
    xlab="Number of Gears", 
    col=cols,
    xlim=c(0,5))

# legend
legend("bottomright", 
   legend = rev(rownames(counts)), #in order from top to bottom
   fill = rev(cols), # reorders so legend order matches graph
   title = "Test01")
```

---

```{r}
#
cols =c("#80b1d3","#66c2a5","#fb8072") # blue, green, red

#
barplot(
    t(counts), 
    main="Car Distribution by Gears and VS",
    xlab="Number of Gears", 
    col=cols,
    xlim=c(0,5))

# legend
legend("bottomright", 
   legend = rev(colnames(counts)), #in order from top to bottom
   fill = rev(cols), # reorders so legend order matches graph
   title = "Test02")
```

---
# Histogram


---
# Scatter Plot & Matrix Plot

---
# Box Plot

